Behavior Driven Development in Haskell

### 2012-05-29 paper.tex
Comment change
Change a comment

\begin{quote}
    sol: We e.g. say ill-behaved Monoid instance.  So is
    ``behavior'' really a bad word?  But I agree that some people in
    the community might associated it with something imperative.

    One might also argue that ``should'' is not very mathematical, but
    it is common language when we talk about mathematics.  E.g. Brent
    Yorgey uses ``should'' a lot in the Typeclassopedia (e.g. ``\ldots
    {\tt Alternative} should satisfy the monoid laws\ldots'')
\end{quote}

@@

\begin{quote}
    \emph{sol: I think the comment contains properties.  So the
    argumentation makes not really sense?}
\end{quote}

>>>>

\begin{quote}
    sol: We e.g. say ill-behaved Monoid instance.  So is
    ``behavior'' really a ``bad'' word?  But I agree that some people in
    the community might associated it with something imperative.

    One might also argue that ``should'' is not very mathematical, but
    it is common language when we talk about mathematics.  E.g. Brent
    Yorgey uses both ``should'' and ``behave'' a lot in the
    Typeclassopedia (e.g. ``\ldots {\tt Alternative} should satisfy
    the monoid laws\ldots'')
\end{quote}

@@

\begin{quote}
    \emph{sol: I think the Haddock comment only contains properties.
    So the argumentation is shaky?}
\end{quote}
